# (APPENDIX) Appendix {-}

#  Appendix - E-device Survey    {#appx_1}

## Survey Questions 

The IEP electronic data entry survey was distributed on June 15, 2022 and responses compiled on August 1, 2022. This survey may be downloaded from the following link:

```{r e_surv, echo = FALSE, include=TRUE, message=FALSE, warning=FALSE }
xfun::embed_file("C:/Users/KAlstad/Kar_Docs/ProjectMangmt/e-Devices/IEP_Edevice_Survey.pdf")
```

## Survey Responses  

The survey responses were separated into responses from experienced e-device users and responses from non-experienced e-device users.


### Responses from Experienced E-device Users   




```{r esurvdat, echo = FALSE, include=TRUE, message=FALSE, warning=FALSE}

source("setup.R")

# Read in data from experience folks #
Exp <- Survey3 %>% filter(grepl('I am currently',dev_exp))  %>%  select(Agency, field_app,   what_hard,  what_soft, yr_reasons )

# Read in data from folks seeking solutions #
Looking <- Survey3 %>% filter(grepl("I am interested" ,dev_exp)|grepl(" researching" ,dev_exp))  %>%  select(Agency,  field_app,   type_data, key_challenges, dev_consid )

# Read in data from folks who would never use e-devices #
NoWay <- Survey3 %>% filter(grepl("e-devices will NOT work" ,dev_exp))  %>%  select(Agency, field_app, type_data_nohope, whathaveyoutried,   yr_reasons, reas_nodevice )


Features <- Survey3 %>% select(Agency, field_app, type_data, type_data_nohope, hrdwr_feachz,sftwr_feachz,other_feachz,extern_contact)


```




```{r e_surv2, echo = FALSE, include=TRUE, message=FALSE, warning=FALSE,, out.width='80%', fig.asp=.75, fig.align='left' }

library(kableExtra)

kable(Exp, format = "html", escape = F, 
      col.names = c("Affiliation","Your Field Application", "What Hardware Using?", "What Software Using?","Key Reasons"), 
      caption = 'Responses from Experience Users', booktabs = TRUE,
      table.attr="table thead th { position: sticky;
  background: white;
  z-index: -100;
  top: calc(var(--line-height) * 1px);}") %>%
  
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE,  font_size = 20) %>%
  kable_paper() %>% 
  column_spec(1, width_min = "3cm", bold = TRUE, italic = F) %>%
  column_spec(1, width_max = "3.5cm", bold = TRUE, italic = F) %>%
  column_spec(2, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(2, width_max = "7cm", bold = F, italic = F) %>%
  column_spec(3, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(3, width_max = "7cm", bold = F, italic = F) %>%
  column_spec(4, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(4, width_max = "7cm", bold = F, italic = F) %>%
  column_spec(5, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(5, width_max = "7cm", bold = F, italic = F) %>%
  scroll_box(width = "1200px", height = "600px")

```



#### Responses from Non-Experienced Seeking E-Solutions  


```{r e_surv3, echo = FALSE, include=TRUE, message=FALSE, warning=FALSE, out.width='80%', fig.asp=.75, fig.align='left' }

library(kableExtra)

Look2 <- Looking %>% select(-field_app)

kable(Look2, format = "html", escape = F, 
      col.names = c("Affiliation","Type of Data", "Key Challenges", "Device Considering"), 
      caption = 'Responses from Non-Experienced Seeking E-Solutions', booktabs = TRUE, align =  "l") %>%
  
  kable_styling(bootstrap_options = c("striped", "hover"),full_width = FALSE,  font_size = 20) %>%
  kable_paper() %>% 
  column_spec(1, width_min = "3cm", bold = TRUE, italic = F, ) %>%
  column_spec(1, width_max = "3.5cm", bold = TRUE, italic = F) %>%
  column_spec(2, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(2, width_max = "7cm", bold = F, italic = F) %>%
  column_spec(3, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(3, width_max = "7cm", bold = F, italic = F) %>%
  column_spec(4, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(4, width_max = "7cm", bold = F, italic = F) %>%
  scroll_box(width = "900px", height = "600px")

```










