# (PART\*) Executive Summary {-}

# Summary 


## **Take Home Message:** {-}

**IEP should transition to electronic data entry in order to improve efficiency and data quality.**

Digital data entry methods facilitate more accurate and rapid reporting of survey data, as compared to paper data sheets, by reducing field entry errors, eliminating manual entry QC checks, and improving overall processing efficiency. 


## **Problem:** {-}

**IEP still uses paper data sheets for most surveys.** Most IEP surveys still use paper datasheets for data collection.  Paper datasheets increase transcription and handwriting errors, increase data transfer time, and increase potential for data loss when compared to electronic data sheets.

**IEP survey leads have significant questions about electronic data entry methods.** Several surveys have considered different data entry software and/or hardware devices for collecting field data, but these tools have not been been broadly adopted due to lack of available information about which tools are most appropriate for survey applications.  



## **Methods:** {-}

The DUWG formed a sub-team and carried out the following steps:

1. **Polled IEP survey teams** to learn what digital data entry tools are currently used within the IEP network; 
2. **Evaluated the top software tools** with interviews/presentations from experienced users and product vendors; 
3. **Conducted software trials** using apps specifically configured for IEP survey data collections;
4. **Developed an open-document forum** for exchange of technical information on e-devices across IEP;
5. **Summarized pros and cons** of the top e-device software options.


## **Solutions:** {-}

Two tools were developed to promote the transition to electronic data entry methods:

- Summarized and expanded listings of the specific pros and cons of each of the top data entry software apps (Table 1 below)

- An open-access html document and Github repository for information related to electronic field data entry software/hardware for IEP Survey applications (Link to [Github repo](https://github.com/InteragencyEcologicalProgram/e-device) and [E-device document Introduction](#intro))


## **Takeaway:** {-}

Adopting digital data entry protocols will require time to develop the field data entry software, establish procedures to transfer data to central database, and train survey staff to use these new tools. In addition, IEP surveys will have to budget for the purchase and maintenance of mobile field devices, data loggers and/or electronic fish measurement boards. **In the long term, the savings in time and effort with the reduction in data entry and post-collection processing will significantly outweigh equipment and training time expenditures.**


NOTE: This Executive Summary was shared with IEP Coordinators Team in Sept of 2023. 
```{r e_surv, echo = FALSE, include=TRUE, message=FALSE, warning=FALSE }
library(here)
xfun::embed_file(c("docs/ExecSumm_edevice_Sept2023.pdf"))
```


## **Table 1:** {-}

<!-- # specifying font style for bold because H3 does not render bold "**" option-->
::: {#Tab1  style="font-size:18px; font-family: Segoe UI;"} 
**Top software applications used by IEP for field data entry with the most notable* pros and cons for each criteria category.**  The criteria used for comparison are described here [criteria category](#crittop). 
:::

*Note: Categories without a specified Pro or Con indicated mean that app meets basic requirements for survey data collection for that category.

*Note: Apps are listed in order reviewed by the DUWG sub-team.

```{r procon, echo = FALSE, include=TRUE, message=FALSE, warning=FALSE,  tab.cap=NULL, out.width='100%', tab.asp=.75, tab.align='left'}

library(kableExtra)
library(dplyr)
library(here)

# 'The top software tools used for field data entry are listed and the Pros and Cons of each tool are briefly described.'

# Replace NAs with empty strings 
proscons[is.na(proscons)] <- ""

# Group by category column and collapse repeating values
proscons %>%
  group_by(Software) %>%
  mutate(Software = ifelse(duplicated(Software), "", Software))  %>%

#caption = ".",
  
kable(proscons, format = "html", escape = F,  booktabs = TRUE, align='l') %>%
  kable_paper() %>% 
  footnote(general = "*Categories without a specified Pro or Con indicated mean that app meets basic requirements for survey data collection for that category.", general_title = "")%>%
  kable_styling(full_width =FALSE, fixed_thead = TRUE, font_size = 18) %>%
  #column_spec(1, width_min = "4cm", bold = TRUE, italic = F) %>%
  column_spec(1, width_max = "4.5cm", bold = TRUE, italic = F) %>%
  #column_spec(2, width_min = "6cm", bold = F, italic = F) %>%
  column_spec(2, width_max = "7cm", bold = F, italic = F) %>%
  #column_spec(3, width_min = "10cm", bold = F, italic = F) %>%
  column_spec(3, width_max = "10cm", bold = F, italic = F) %>%
  scroll_box(width = "800px")

```




